Multiplex stream graphs

### 2019-05-28 tex/main sauv 2809.tex
updates src + tex

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{schemas/edgesCat.jpg}
		\caption{Illustration with our example of coupling edges, intra-layer edges and inter-layer edges}
		\label{exIntraInter}
	\end{figure}
   	The {\em multilayer graph at time t} $M_t$ is $M_t = (V_{M,t}, E_{M,t},V_t,{\cal L}_t)$ with :
    \begin{itemize}
		\item $V_{M,t} = \{(u,\alpha)| (t,u,\alpha)\in W_M\}$
		\item $E_{M,t} = \{(u,\alpha,v,\beta) | (t,u,\alpha,v,\beta) \in E_M\}$
		\item $V_t = {u | (t,u) \in V}$
		\item ${\cal L}_t = {L_i,t}_{i=1}^d, L_{i,t}=(\alpha)_i, t\in T_\alpha$
    \end{itemize}

	\begin{figure}	
		\begin{minipage}{0.49\linewidth}
			\includegraphics[width=\textwidth]{schemas/pauset.jpg}
		\end{minipage}
		\begin{minipage}{0.49\linewidth}
			\includegraphics[width=\textwidth]{schemas/pausetproj.jpg}
		\end{minipage}
		\caption{Our multilayer example at time $t=5$}
	\end{figure}

@@

	We can then define the density of the multilayer graph. Notice first that the density measures the rate of connectivity, and so depending to the type of system we study, the definition can change. If some connections are forbidden, we will ignore it in the density. We name $C \in V_M\times V_M$ the set of possible connections in the mutlilayer. If some connections are automatics (like the ones between the same node in different layers), we don't take it into account too.
	\[
		\delta_M (M) = \frac{|E_M|}{|\{\text{"possible connections"}\}|}
	\]

@@

		In the multilayer graphs, it is a more tricky question to know who are the neighbours of a node. In many multiplexes, the nodes-layers corresponding to the same node are linked together with an "invisible" connection. The main question, should be of course : "what do we want to measure ?" We will give a few example of different situation and the definition of the degree associated.

@@

		We can resume as follows the notion of the degree of a node : it is the number of nodes of the neighbours cluster. The question is the what neighbours do we take and what is their nature ?

		As we know the number of nodes in a multilayer, the degree of a node is then : 
		$$
			d(v) = 
		$$

>>>>

	\begin{figure}[h]
		\centering
		\includegraphics[width=\textwidth]{schemas/edgesCat.jpg}
		\caption{Illustration with our example of coupling edges, intra-layer edges and inter-layer edges}
		\label{exIntraInter}
	\end{figure}
   	The {\em multilayer graph at time t} $M_t$ is $M_t = (V_{M,t}, E_{M,t},V_t,{\cal L}_t)$ with :
    \begin{itemize}
		\item $V_{M,t} = \{(u,\alpha)| (t,u,\alpha)\in W_M\}$
		\item $E_{M,t} = \{(u,\alpha,v,\beta) | (t,u,\alpha,v,\beta) \in E_M\}$
		\item $V_t = {u | (t,u) \in V}$
		\item ${\cal L}_t = {L_i,t}_{i=1}^d, L_{i,t}=(\alpha)_i, t\in T_\alpha$
    \end{itemize}

	\begin{figure}[h]
		\begin{minipage}{0.49\linewidth}
			\includegraphics[width=\textwidth]{schemas/pauset.jpg}
		\end{minipage}
		\begin{minipage}{0.49\linewidth}
			\includegraphics[width=\textwidth]{schemas/pausetproj.jpg}
		\end{minipage}
		\caption{Our multilayer example at time $t=5$}
	\end{figure}

@@

	We can then define the density of the multilayer graph. Notice first that the density measures the rate of connectivity, and so depending to the type of system we study, the definition can change. If some connections are forbidden, we will ignore them in the density. We name $C \in V_M\times V_M$ the set of possible connections in the mutlilayer. If some connections are automatics (like the ones between the same node in different layers), we don't take it into account too.
	\[
		\delta_M (M) = \frac{|E_M|}{|\{\text{"possible connections"}\}|}
	\]

@@

		In the multilayer graphs, it is a more tricky question to know who are the neighbours of a node. In many multiplexes, the nodes-layers corresponding to the same node are linked together with an "invisible" connection. The main question should be of course : "what do we want to measure ?" We will give a few examples of different situation and the definition of the degree associated.

@@

		We can resume as follows the notion of the degree of a node : it is the number of nodes of the neighbours cluster.

		As we know the number of nodes in a multilayer, the degree of a node is then : 
		$$
			d(v) = N_n(\{\text{neighbours of v}\})
		$$

		The question is : the what neighbours do we take and what is their nature ?

		In a stream graphs, $(t_1,v)$ and $(t_2,u)$ are neighbours if for all $t$ in $[t_1,t_2]$, $(t,u,v)$ belongs to $E$.

		In a multilayer stream graph, $(t_1,v,\alpha)$ and $(t_2,u,\beta)$ are neighbours if for all $t$ in $[t_1,t_2]$, $(t,(u,\alpha),(v,\beta))$ belongs to $E_M$.

	\section{Centralities}

		Many types of centralities has been defined for classical graphs, and not all of them are adapted to all problems. We will see a few of them, how we can adapt them to the multilayer stream graphs and give some examples in which they can be usefull.

		\subsection{Betweenness centrality}

		Betweenness	centrality has been defined as follows in graphs : it measures how much a node is involved in the shortest between two nodes.

		\[
			{\cal C}(u) = \sum_{v,w \in V} \frac{\sigma(v,w,u)}{\sigma(v,w)} 
			\]
			\[
			\sigma(v,w) = \text{number of shortest paths between v and w} 
			\]\[
			\sigma(v,w,u) = \text{number of path containing u in the shortest paths between v and w.}
		\]

		In multilayer stream graphs, we can apply this definition to the aggregated network and the underlying network.
